How to use flowCore package

### 2006-11-29 inst/doc/HowTo-flowCore.Rnw
move fcs files from data to extdada modify the vignette and man pages
git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/flowCore@21315 bc3139a8-67e5-0310-9ffc-ced21a209358

\section{Methodology}
\subsection{Reading data}
We first load the libraries and read the data into R as FCS object 
(rflowcyt data format). Note than this small example works for cytoFrame object. 
<<load library>>=
library("flowCore")
@ 
<<load data,echo=FALSE,results=hide>>=
fcs.loc <- system.file("data", package="flowcore")
file.location <- paste(fcs.loc, dir(fcs.loc), sep="/")
b08 <- read.FCS(file.location[1])
e07 <- read.FCS(file.location[2])
f06 <- read.FCS(file.location[3])
@
\begin{verbatim}
> fcs.loc <- system.file("data", package="flowcore")
> file.location <- paste(fcs.loc, dir(fcs.loc), sep="/")
> b08 = read.FCS(file.location[1])
> e07 = read.FCS(file.location[2])
> f06 = read.FCS(file.location[3])
\end{verbatim}

@@

<<SelectNonDebris,eval=TRUE,echo=FALSE,results=hide>>=
min1 <- c(200,0)
max1 <- c(800,800)
ilter1 <- new("rectangleGate",filterId="Nondebris",parameters=c("FSC-H","SSC-H"),
  min=min1,max=max1)

>>>>

\section{Methodology}
\subsection{Reading data}
We first load the libraries and read the data into R as FCS object 
(rflowcyt data format). Note than this small example works for cytoFrame object. 
<<load library>>=
library("flowCore")
@ 
<<load data,echo=FALSE,results=hide>>=
fcs.loc <- system.file("extdata", package="flowCore")
file.location <- paste(fcs.loc, dir(fcs.loc), sep="/")
b08 <- read.FCS(file.location[1])
e07 <- read.FCS(file.location[2])
f06 <- read.FCS(file.location[3])
@
\begin{verbatim}
> fcs.loc <- system.file("extdata", package="flowCore")
> file.location <- paste(fcs.loc, dir(fcs.loc), sep="/")
> b08 = read.FCS(file.location[1])
> e07 = read.FCS(file.location[2])
> f06 = read.FCS(file.location[3])
\end{verbatim}

@@

<<SelectNonDebris,eval=TRUE,echo=FALSE,results=hide>>=
min1 <- c(200,0)
max1 <- c(800,800)
filter1 <- new("rectangleGate",filterId="Nondebris",parameters=c("FSC-H","SSC-H"),
  min=min1,max=max1)
